\section{Private Methods}

These methods can only be used by the classes {\tt ChromosomeT\_num}, 
{\tt ChromosomeT}$<$Type$>$, {\tt Individual} and {\tt Population}.

\subsection{Generating Methods}

%---------------------------------------------------------------------------%
\index{clone!( )}
    \setConstInstance   
    \printEmptyMethodReturn
    {Chromosome$\ast$} 
    {clone}
    {Returns a copy of the current chromosome {\em this}.}
    {Pointer to copy of {\em this}.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{empty!( )}
    \printEmptyMethodReturn
    {Chromosome$\ast$} 
    {empty}
    {Returns a new empty chromosome.}
    {Pointer to the new chromosome.}
%---------------------------------------------------------------------------%

\clearpage

\subsection{Input- and Output Methods}

%---------------------------------------------------------------------------%
\index{writeDataTo!( ostream\& os )}
    \printMethodWithOneParam
    {void} 
    {writeDataTo}
    {ostream\&} 
    {os} 
    {Output stream.}
    {Writes the content of {\em this} to the output stream {\em os}.
The single alleles of the chromosome will be separated by a tab character.}
    {None.}
    {This function is not included in this version.}
    \setNormalInstance
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{writeTo!( ostream\& os )}
    \setConstInstance
    \printMethodWithOneParam
    {void}
    {writeTo}
    {ostream\&} 
    {os} 
    {Output stream.}
    {Writes the content of {\em this} to the output stream {\em os},
that means the type, size and the allele values will be send to 
{\em os}. The single alleles will be separated by a tab
character.}
    {None.}
    {None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{readDataFrom!( istream\& is )}
    \setNormalInstance
    \printMethodWithOneParam
    {void} 
    {readDataFrom}
    {istream\&} 
    {is} 
    {Input stream.}
    {The values of the single alleles of {\em this} will be replaced
by new values, read from the input stream {\em is}.}
    {None.}
    {This function is not included in this version.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{readFrom!( istream\& is )}
    \setNormalInstance
    \printMethodWithOneParam
    {void}
    {readFrom}
    {istream\&} 
    {is}
    {Input stream.}
    {Replaces the chromosome {\em this} with the values, that will be
read from the input stream {\em is}. The data must have the 
following format:\\
     ``{\tt ChromosomeT$<$}'',\\
     {\tt Type of the chromosome},\\ 
     ``{\tt $>$(}'',\\
     {\tt Number of chromosome alleles},\\ 
     ``{\tt )}'',\\ 
     {\tt Newline},\\
     {\tt Values of the single alleles, 
      separated by a space or tab character}.\\
     For example the data ``{\tt ChromosomeT< int >(5)\\n 1 2 3 4 5}''  
     is written into a file to create a chromosome of type {\tt int}
     with the five alleles 1, 2, 3, 4 and 5.}
    {None.}
    {None.}
%---------------------------------------------------------------------------%









