\begin{thebibliography}{55}
 
    \bibitem{Foundations}
    {\em Foundations of Genetic Algorithms}, G.J.E. Rawlings (Editor),
    Morgan Kaufmann Publishers, San Mateo, CA, 1991.

    \bibitem{ICEC96}
    {\em Proceedings of the 1996 IEEE Internal Conference on Evolutionary 
    Computation (ICEC '96)}.
   
    \bibitem{First}
    {\em Proceedings of the First International Conference on Genetic 
    Algorithms and Their Applications} (ICGA 1985), published by
    J.J. Grefenstette, Pittsburgh, PA, Juli 24-26 1985, Carnegie-Mellon 
    University, Lawrence Erlbaum Associates (Hillsdale, NJ, 1988).

    \bibitem{Third}
    {\em Proceedings of the Third International Conference on Genetic 
    Algorithms} (ICGA 1989), published by J.D. Schaffer, July 4-7, 
    San Mateo, CA, 1989, George Mason University, Morgan Kaufmann 
    Publishers Inc.

    \bibitem{Eshelman95}
    {\em Proceedings of the Sixth International Conference on Genetic
    Algorithms}, published by L.J. Eshelman, 1995.

    \bibitem{Goldberg}
    {\em A comparative analysis of selection schemes used in genetic
    algorithms}, by D.E. Goldberg and K. Deb published at pages
    69 to 93 in \cite{Foundations}.

    \bibitem{Baeck}
    {\em Evolutionary Algorithms in Theory and Practice}, 
    dissertation thesis by T. B\"ack, University of Dortmund, 
    Department of Computer Science, February 1994.

    \bibitem{EALibRef}
    {\em EALib: A \cpp\ class library for evolutionary algorithms}, 
    version 1.5, 2000, by M. Kreutz, B. Sendhoff and C. Igel, 
    Institut f\"ur Neuroinformatik, Ruhr-Universit\"at Bochum.

    \bibitem{Baker}
    {\em Adaptive Selection methods for genetic algorithms}, by J.E. Baker, 
    published at the pages 101 to 111 in \cite{First}.

    \bibitem{AlgoWork}
    {\em How genetic algorithms work: A critical look at implicit
    parallelism}, by J.J. Grefenstette and J.E. Baker, published
    at the pages 20 to 27 in \cite{Third}. 

    \bibitem{Whitley}
    {\em The genitor algorithm and selection pressure:
    Why rank-based allocation of reproductive trials is best} by L.D.
    Whitley, published at the pages 116 to 121 in \cite{Third}.

    \bibitem{Fogel}
    {\em Evolutionary Computation: Toward a New Philosophy of
    Machine Intelligence} by D.B. Fogel, IEEE Press, 1995.

    \bibitem{Search}
    {\em Genetic Algorithms in Search, Optimization, and Machine Learning}, 
    by D.E. Goldberg, Addison-Wesley Publishing Company, Inc., Reading, MA, 
    1989.

    \bibitem{Jong}
    {\em An Analysis of the Behaviour of a Class of Genetic Adaptive
    Systems} by K.A.D. Jong, Dept. Computer and Communication Sciences,
    University of Michigan, 1975, Diss. Abstr. Int. 36(10), 5140B,
    University Microfilms No. 76-9381.

    \bibitem{GSA}
    {\em On the Adaptation of Arbitrary Normal Mutation Distributions
    in Evolution Strategies: The Generating Set Adaptation},
    by N. Hansen, A. Ostermeier and A. Gawelczyk, published at the pages
    57 to 64 in \cite{Eshelman95}. 

    \bibitem{CMA}
    {\em Adapting Arbitrary Normal Mutation. Distributions in Evolution
    Strategies: The Covariance Matrix Adaptation}, by N. Hansen and A. 
    Ostermeier, appeared at the pages 312 to 317 in \cite{ICEC96}.

    \bibitem{MSR}
    {\em Schrittweitenadaptation in der Evolutionsstrategie mit einem
    ent\-sto\-chasti\-sier\-ten Ansatz}, by A. Ostermeier, dissertation thesis, 
    Technische Universit\"at Berlin, Fachbereich 6, 1997.

    \bibitem{NRC}
    {\em Numerical Recipes in C ( Second Edition )}, by William
    H. Press, Saul A. Teukolsky, William T. Vettering and Brian
    P. Flannery, Cambridge University Press, 1992. \label{NRC}

\end{thebibliography}
