\subsection{Information Retrieval Methods}

%---------------------------------------------------------------------------%
\index{size!( )}
\setConstInstance
\printEmptyMethodReturn
{unsigned}
{size}
{Returns the number of chromosome in {\em this}.}
{Number of chromosomes in {\em this}.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{totalSize!( )}
\setConstInstance
\printEmptyMethodReturn
{unsigned}
{totalSize}
{Returns the number of all alleles of the chromosomes in {\em this}.}
{The whole number of alleles in {\em this}.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{fitnessValue!( )}
\setConstInstance
\printEmptyMethodReturn
{double}
{fitnessValue}
{Returns the fitness value of the current individual {\em this}.}
{Fitness value of {\em this}.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{getAge!( )}
\setConstInstance
\printEmptyMethodReturn
{unsigned}
{getAge}
{Returns the age of {\em this}, i.e. the generation {\em this} is from.}
{Age of {\em this}.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{needEvaluation!( )}
\setConstInstance
\printEmptyMethodReturn
{bool}
{needEvaluation}
{Returns the status of the {\em evalFlg}, i.e. whether the individual must 
 be evaluated.}
{Status of {\em evalFlg}:\\
 {\em true} - An evaluation of {\em this} is necessary,\\
 {\em false} - The individual needs no evaluation.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{selectionProbability!( )}
\setConstInstance
\printEmptyMethodReturn
{double}
{selectionProbability}
{Returns the selection probability for {\em this}.}
{The selection probability of {\em this}.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{isFeasible!( )}
\setConstInstance
\printEmptyMethodReturn
{bool}
{isFeasible}
{Returns whether {\em this} is a possible solution for the
 current optimization problem.}
{Status of the {\em feasible}-flag:\\
 {\em true} - The individual is a possible solution,\\
 {\em false} - The individual cannot used as solution.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{numberOfCopies!( )}
\setConstInstance
\printEmptyMethodReturn
{unsigned}
{numberOfCopies}
{Returns the number of reproductions of {\em this} that occured
 during the last selection.}
{Number of reproductions of {\em this}.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{isElitist!( )}
\setConstInstance
\printEmptyMethodReturn
{bool}
{isElitist}
{Returns the status of the {\em elitist}-flag, i.e. whether {\em this} 
 was chosen as elite individual during the last selection.}
{Status of the {\em elitist}-flag:\\
 {\em true} - The individual was chosen as elitist,\\
 {\em false} - The individual was not chosen.}
%---------------------------------------------------------------------------%

