\section{Internal Class {\em DerandomConst}}

The class {\tt ChromosomeT$<$ double $>$} contains an internal
subclass, that is used for the execution of the self-adaptative
method {\em Derandom}. The variables and methods that are
part of the subclass can not be called and modified directly, but
the {\tt ChromosomeT$<$ double $>$} class owns some methods for this
purpose. 

\subsection{Internal Variables of {\em DerandomConst}}

\begin{itemize}
\item {\em dim} - 
 Dimension of the chromosome. Not initialized. 
\index{dim (Variable)}

\item {\em C} -
 Period of cumulation, initialized with $\frac{1.0}{\sqrt{n}}$.
\index{C (Variable)}

\item {\em Cu} -
 Normalizing factor for the sum vector {\em s}, initialized with 
 $\sqrt{\frac{2.0 - C}{C}}$.
\index{Cu (Variable)}

\item {\em Crr} -
 Period of cumulation for the preference direction, initialized with 
 $\frac{3.0}{n}$. 
\index{Crr (Variable)}

\item {\em Beta} -
 Damping of the global stepsize adaptation, initialized 
 with $\frac{1.0}{\sqrt{n}}$.
\index{Beta (Variable)}

\item {\em BetaI} -
 Damping of the individual stepsize adaptation, initialized with
 $\frac{1}{n}$.
\index{BetaI (Variable)}

\item {\em BetaR} -
 Damping of the direction, initialized with $\frac{1.0}{\sqrt{4n}}$. 
\index{BetaR (Variable)}

\item {\em ChiN} -
 Expectation value for the $\chi_n$-distribution,\\ initialized with
 $\sqrt{n}(1 - \frac{1}{4n} + \frac{1}{21n^2})$.
\index{ChiN (Variable)}

\item {\em Chi1} -
 Expectation value for the $\chi_1$-distribution, initialized with
 $\sqrt{\frac{2}{\pi}}$.
\index{Chi1 (Variable)}

\end{itemize}

\clearpage

\subsection{Internal Methods of {\em DerandomConst}}

%---------------------------------------------------------------------------%
\index{DerandomConst!( unsigned n )}
\setNormalInstance
\printMethodWithOneParam
{}
{DerandomConst}
{unsigned}
{n}
{Initializing value for the dimension.}
{Initializes the internal variables of class {\em DerandomConst}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{nobj!( )}
\setNormalInstance
\printEmptyMethodReturn
{unsigned}
{nobj}
{Returns the dimension value.}
{The dimension value.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{npar!( )}
\setNormalInstance
\printEmptyMethodReturn
{unsigned}
{npar}
{Returns the number of necessary parameters for the {\em Derandom} method.}
{Number of necessary parameters.}
%---------------------------------------------------------------------------%





