\subsection{Constructors}

%---------------------------------------------------------------------------%
\index{Individual!( )}
\setNormalInstance
\printEmptyMethod
{Individual}
{Generates an empty individual.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( unsigned n )}
\setNormalInstance
\printMethodWithOneParam
{explicit}
{Individual}
{unsigned}
{n}
{Number of chromosomes.}
{Generates a new individual and reserves memory for
 {\em n} chromosomes of type {\tt char}.}
{None.}
{{\em explicit} = Implicit calls of the constructor in assignments of type
 {\tt Individual} {\em ind} = $<$Value$>$ are not possible.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{Individual!( unsigned n, const Chromosome\& chrom )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{n}{unsigned}{Number of clones.}
\setParamTwo{chrom}{const Chromosome\&}{Chromosome to be cloned.}
\printMethodWithParamsSaved
{}
{}
{Individual}
{Generates an individual that consists of {\em n} clones of the
 chromosome {\em chrom}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0 )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Chromosome\&}
{chrom0}
{Chromosome, to be cloned.}
{Generates an individual that consists of the chromosome {\em chrom0}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0, const Chromosome\& chrom1 )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{chrom0}{const Chromosome\&}{First chromosome, which 
is part of the new individual.}
\setParamTwo{chrom1}{const Chromosome\&}{Second chromosome, which 
is part of the new individual.}
\printMethodWithParamsSaved
{}
{}
{Individual}
{Generates an individual that consists of the chromosomes {\em chrom0} 
 and {\em chrom1}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0 .. chrom2 )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Chromosome\&}
{chrom0 .. chrom2}
{Chromosomes that make up the new individual.}
{Generates an individual that consists of the chromosomes
 {\em chrom0} to {\em chrom2}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0 .. chrom3 )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Chromosome\&}
{chrom0 .. chrom3}
{Chromosomes, that make up the new individual.}
{Generates an individual that consists of the chromosomes {\em chrom0}
 to {\em chrom3}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0 .. chrom4 )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Chromosome\&}
{chrom0 .. chrom4}
{Chromosomes, that make up the new individual.}
{Generates an individual that consists of the chromosomes {\em chrom0} to
 {\em chrom4}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0 .. chrom5 )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Chromosome\&}
{chrom0 .. chrom5}
{Chromosomes, that make up the new individual.}
{Generates an individual that consist of the chromosomes {\em chrom0}
 to {\em chrom5}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0 .. chrom6 )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Chromosome\&}
{chrom0 .. chrom6}
{Chromosomes, that make up the new individual.}
{Generates an individual that consist of the chromosomes {\em chrom0} to
 {\em chrom6}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( const Chromosome\& chrom0 .. chrom7 )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Chromosome\&}
{chrom0 .. chrom7}
{Chromosomes, that make up the new individual.}
{Generates an individual that consist of the chromosomes {\em chrom0}
 to {\em chrom7}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{Individual!( const vector$<$ Chromosome$\ast$ $>$\& chrom )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const vector$<$ Chromosome* $>$\&}
{chrom}
{The vector of chromosomes.}
{Generates an individual that consists of the chromosomes stored in 
 vector {\em chrom}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{Individual!( const Individual\& indiv )}
\setNormalInstance
\printMethodWithOneParam
{}
{Individual}
{const Individual\&}
{indiv}
{Individual.}
{Generates an individual that is a copy of {\em indiv} including
 the internal class variables.}
{None.}
{None.}
%---------------------------------------------------------------------------%
