\subsection{Structure Modifying Methods}

%---------------------------------------------------------------------------%
\index{resize!( unsigned n )}
\setNormalInstance
\printMethodWithOneParam
{void}
{resize}
{unsigned}
{n}
{New size of the population.}
{Changes the size of the population to the new value {\em n}. If {\em n}
 is less than the old size {\em m} of {\em this}, then all {\em m} - {\em n}
 individuals at the end of {\em this} will be removed, if {\em n} is greater
 than {\em m}, then {\em n} - {\em m} new empty individuals will be
 appended at the end of {\em this}. All other individuals will remain
 unchanged.} 
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{replace!( unsigned i, const Individual\& ind )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i}{unsigned}{Index of the individual inside of {\em this}
to be replaced. {\em i} must be less than the number of individuals
in {\em this}, otherwise the method will be aborted with an error message.}
\setParamTwo{ind}{const Individual\&}{Individual to replace the
old one.}
\printMethodWithParamsSaved
{void}
{}
{replace}
{Replaces individual number {\em i} by the individual {\em ind}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{replace!( unsigned i, const Population\& pop )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i}{unsigned}{Index of the first individual in {\em this}.}
\setParamTwo{pop}{const Population\&}{Population.}
\printMethodWithParamsSaved
{void}
{}
{replace}
{Replaces all individuals inside of {\em this}, beginning with the one
 at position number {\em i}, by the individuals of the population {\em pop}.
 If the number of individuals inside of {\em pop} is greater than the
 number of individuals in {\em this} beginning at position {\em i}, then
 the method will be aborted with an error message.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{insert!( unsigned i, const Individual\& ind )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i}{unsigned}{Index at which {\em ind} is inserted
in {\em this}. {\em i} must be at most as great as the number of
individuals in {\em this}, otherwise the method will be aborted with
an error message.}
\setParamTwo{ind}{const Individual\&}{Individual to be
inserted.}
\printMethodWithParamsSaved
{void}
{}
{insert}
{Inserts the individual {\em ind} at index {\em i} inside the population
 {\em this}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{insert!( unsigned i, const Population\& pop )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i}{unsigned}{Index of {\em this} where the first
individual of {\em pop} is inserted. {\em i} must be at most
as great as the number of individuals in {\em this}, otherwise the 
method will be aborted with an error message.}
\setParamTwo{pop}{const Population\&}{Population, with the individuals that
will be inserted into {\em this}.}
\printMethodWithParamsSaved
{void}
{}
{insert}
{Inserts all individuals of {\em pop} into {\em this}, beginning at
 position {\em i}.} 
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{append!( const Individual\& ind )}
\setNormalInstance
\printMethodWithOneParam
{void}
{append}
{const Individual\&}
{ind}
{The individual to be appended to {\em this}.}
{Appends individual {\em ind} at the end of {\em this}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{append!( const Population\& pop )}
\setNormalInstance
\printMethodWithOneParam
{void}
{append}
{const Population\&}
{pop}
{Population.}
{Appends all individuals of Population {\em pop} at the end of 
 population {\em this}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{remove!( unsigned i )}
\setNormalInstance
\printMethodWithOneParam
{void}
{remove}
{unsigned}
{i}
{Index of the individual that is to be removed from {\em this}.
 {\em i} must be less than the number of individuals in {\em this},
 otherwise the method will be aborted with an error message.}
{Removes individual number {\em i} from {\em this}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{remove!( unsigned from, unsigned to )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{from}{unsigned}{Index of the first individual of {\em this}
to be removed. {\em from} must be less than the number of individuals
in {\em this}, otherwise the method will be aborted with an error message.
Additionally, {\em from} must be at most as great as {\em to} or
no individual will be removed from {\em this}.}
\setParamTwo{to}{unsigned}{Index of the last individual to be
removed from {\em this}. {\em to} must be less than the number of
individuals in {\em this}, otherwise the method will be aborted with
an error message.}
\printMethodWithParamsSaved
{void}
{}
{remove}
{Removes all individuals in the range $[from, to]$ from the
 population {\em this}.}
{None.}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{exchange!( Population\& pop )}
\setNormalInstance
\printMethodWithOneParam
{void}
{exchange}
{Population\&}
{pop}
{Population.}
{Swaps all individuals of {\em pop} with the individuals of {\em this}.
 The populations must contain the same number of individuals, otherwise
 the method will be aborted with an error message.}
{None.}
{None.}
%---------------------------------------------------------------------------%



