\subsection{Structure Changing Methods}

%---------------------------------------------------------------------------%
\index{replace!( unsigned i, const Chromosome\& chrom )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i}{unsigned}{Index of the chromosome of {\em this}, to
be replaced. {\em i} must be less than the number of chromosomes
in {\em this}, otherwise the method will be aborted with an error message.}
\setParamTwo{chrom}{const Chromosome\&}{Chromosome that
replaces the old chromosome in {\em this}.}
\printMethodWithParamsSaved
{void}
{}
{replace}
{Replaces chromosome number {\em i} with the content of chromosome 
 {\em chrom}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{insert!( unsigned i, const Chromosome\& chrom )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i}{unsigned}{Insertion-position in {\em this}.
The maximum value for {\em i} shall be equal to the
number of chromosomes in {\em this}, otherwise the method will be
aborted with an error message.}
\setParamTwo{chrom}{const Chromosome\&}{Chromosome to be inserted
into {\em this}.}
\printMethodWithParamsSaved
{void}
{}
{insert}
{Inserts chromosome {\em chrom} at position {\em i} into {\em this}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{append!( const Chromosome\& chrom )}
\setNormalInstance
\printMethodWithOneParam
{void}
{append}
{const Chromosome\&}
{chrom}
{Chromosome to be appended at the end of {\em this}.}
{Appends the chromosome {\em chrom} at the end of {\em this}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{remove!( unsigned i )}
\setNormalInstance
\printMethodWithOneParam
{void}
{remove}
{unsigned}
{i}
{Index of the chromosome to be removed from {\em this}.
{\em i} must be less than the number of chromosomes in {\em this},
otherwise the method will be aborted with an error message.}
{Removes the chromosome with index {\em i} from {\em this}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{remove!( unsigned from, unsigned to )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{from}{unsigned}{Index of the first chromosome to be
removed. {\em from} must be less than the number of chromosomes in {\em this}
and not greater as {\em to} or the method will be aborted with an
error message.}
\setParamTwo{to}{unsigned}{Index of the last chromosome to be
removed. {\em to} must be less than the number of chromosomes in {\em this}
and not smaller as {\em from} or the method will be aborted with an
error message.}
\printMethodWithParamsSaved
{void}
{}
{remove}
{Removes all chromosomes with indices in the range $[from, to]$.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

