\subsection{Constructors}

Constructors are not directly defined in this class, but in the class
{\tt ChromosomeT\_base}, that is built upon the base class.
Class {\tt Chromosome} is only declared for overloading.\\

%---------------------------------------------------------------------------%
\index{ChromosomeT\_base!( )}
\setNormalInstance
\printEmptyMethod
{ChromosomeT\_base}
{Generates a new empty chromosome of any type and registers it.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{ChromosomeT\_base!( unsigned l )}
\setNormalInstance
\printMethodWithOneParam
{explicit}
{ChromosomeT\_base}
{unsigned}
{l}
{Size of the chromosome.}
{Generates a new empty chromosome of any type and therefore reserves
 memory for {\em l} alleles. The chromosome is registered.}
{None.}
{{\em explicit} = Implicit calls in commands like 
 ``ChromosomeT\_base {\tt chrom} = $<$value$>$'' are not possible.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{ChromosomeT\_base!( unsigned l, const T\& v )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{l}{unsigned}{Size of the chromosome.}
\setParamTwo{v}{const {\sl T}\&}{Initial value for the alleles of the 
chromosome.}
\printMethodWithParamsSaved
{}
{}
{ChromosomeT\_base}
{Generates a new empty chromosome of type {\sl T} with {\em l} alleles
 and initializes the alleles with the value {\em v}. 
 The chromosome is registered.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{ChromosomeT\_base!( const vector$<$ T $>$\& v )}
\setNormalInstance
\printMethodWithOneParam
{}
{ChromosomeT\_base}
{const vector$<$ {\sl T} $>$\&}
{v}
{Vector with values for the initialization of the alleles of the chromosome.}
{Generates a new chromosome of type {\sl T} and the values of {\em v}
 are copied to {\em this}. The chromosome is registered.}
{None.}
{None.}
%---------------------------------------------------------------------------%