\subsection{Recombination Methods}

%---------------------------------------------------------------------------%
\index{recombineDiscrete!( const Chromosome\& dadChrom, const Chromosome\& momChrom )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromosome that must
contain at least one allel, otherwise no recombination will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that
must contain as many alleles as {\em dadChrom}, otherwise the method will
be aborted with an error message. Additionally, {\em momChrom} must
have at least one allele or no recombination will take place.}
    \printMethodWithParamsSaved
        {void}
        {}
        {recombineDiscrete}
        {Randomly recombines the chromosomes {\em dadChrom} and 
{\em momChrom} and stores the result in {\em this}. The probability for
each allele of {\em this} to be either from {\em dadChrom} or
{\em momChrom} is $0.5$. The size of {\em this} will be
adapted to the size of a parent chromosome.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{recombineDiscrete!( Chromosome\& mate )}
    \printMethodWithOneParam
    {void} 
    {recombineDiscrete}
    {Chromosome\&} 
    {mate}
    {Chromosome that will be recombined with {\em this}. {\em mate} must
contain as many alleles as {\em this}, otherwise the method will be
aborted with an error message and {\em mate} must have at least
one allele or no recombination will take place.} 
    {Same as above, but here the chromosomes {\em mate} and {\em this}
itself will be taken as ``parent'' chromosomes. Again the result is stored
in {\em this}. An allele $this_i$ (with $i\ =\ 0..n-1$, $n\ =\ $ 
number of alleles in {\em this}) will contain the value $mate_i$
with probability $0.5$.}
    {None.}
    {None.}
%---------------------------------------------------------------------------%
