\section{Private Methods}

These methods can only be used by the class {\em EvoAlg}.
\index{EvoAlg}

\subsection{Constructors}

%---------------------------------------------------------------------------%
\index{Population!( const vector$<$ Individual $\ast$ $>$\& indvec )}
\setNormalInstance
\printMethodWithOneParam
{}
{Population}
{const vector$<$ Individual $\ast$ $>$\&}
{indvec}
{Vector with individuals that make up the new population.}
{Generates a new population consisting of the individuals that are
 stored in vector {\em indvec}.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\subsection{Initialization Methods}

%---------------------------------------------------------------------------%
\index{selectInit!( )}
\setNormalInstance
\printEmptyMethod
{selectInit}
{Initializes the internal variables of all individuals of the population
 for a following selection method.}
%---------------------------------------------------------------------------%

\clearpage

\subsection{Comparison Methods}

These methods compare two individuals of a population 
and either return the status of this comparison or 
one of the individuals. The methods described here are used as 
auxiliary methods by other major methods.

\vspace{2ex}

%---------------------------------------------------------------------------%
\index{lessFitness!( Individual$\ast$ const\& i1, Individual$\ast$ const\& i2 )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i1}{Individual$\ast$const\&}{Individual 1.}
\setParamTwo{i2}{Individual$\ast$const\&}{Individual 2.}
\printMethodWithParamsSaved
{static bool}
{Status of the fitness comparison:\\
 {\em true} - The fitness of individual {\em i1} is less than the fitness
 of individual {\em i2},\\
 {\em false} - The fitness of individual {\em i1} is greater than or equal
 to the fitness of individual {\em i2}.}
{lessFitness}
{Returns whether the fitness of individual {\em i1} is less than the 
 fitness of individual {\em i2}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{greaterFitness!( Individual$\ast$ const\& i1, Individual$\ast$ const\& i2 )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i1}{Individual$\ast$const\&}{Individual 1.}
\setParamTwo{i2}{Individual$\ast$const\&}{Individual 2.}
\printMethodWithParamsSaved
{static bool}
{Status of the fitness comparison:\\
 {\em true} - The fitness of individual {\em i1} is greater than the fitness
 of individual {\em i2},\\
 {\em false} - The fitness of individual {\em i1} is less than or equal
 to the fitness of individual {\em i2}.}
{greaterFitness}
{Returns whether the fitness of individual {\em i1} is greater than the 
 fitness of individual {\em i2}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{greaterScoreAscending!( Individual$\ast$ const\& i1, Individual$\ast$ const\& i2 )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i1}{Individual$\ast$ const\&}{First individual.}
\setParamTwo{i2}{Individual$\ast$ const\&}{Second individual.}
\printMethodWithParamsSaved
{static bool}
{
 {\em true} - The scaled fitness of individual {\em i1}
              is greater than the scaled fitness of individual {\em i2}
              or the normal fitness of individual {\em i1} is less than
              the normal fitness of individual {\em i2}.\\
 {\em false} - The scaled fitness of individual {\em i1} is less than
               the scaled fitness of individual {\em i2} or the
               normal fitness of individual {\em i1} is greater than
               the normal fitness of individual {\em i2}.}
{greaterScoreAscending}
{Auxiliary method for {\em selectEPTournament}.
 Checks whether the scaled fitness of individual {\em i1} 
 is greater or whether the normal fitness is less than the
 corresponding values of individual {\em i2}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{greaterScoreDescending!( Individual$\ast$ const\& i1, Individual$\ast$ const\& i2 )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{i1}{Individual$\ast$const\&}{First individual.}
\setParamTwo{i2}{Individual$\ast$const\&}{Second individual}
\printMethodWithParamsSaved
{static bool}
{
 {\em true} - The scaled fitness value or the normal fitness value
              is greater than the corresponding values of {\em i2},\\
 {\em false} - The scaled fitness value or the normal fitness value
               is less than the corresponding values of {\em i2}.}
{greaterScoreDescending}
{Auxiliary method for {\em selectEPTournament}.
 Checks whether the scaled or normal fitness of individual {\em i1} 
 is greater than the corresponding values of individual {\em i2}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{best!( Individual\& ind0, Individual\& ind1 )}
\setConstInstance
\setCorrectWidthThree{8pt}
\setParamOne{ind0}{Individual\&}{First individual.}
\setParamTwo{ind1}{Individual\&}{Second individual.}
\printMethodWithParamsSaved
{Individual\&}
{The individual with the ``better'' fitness according to 
 {\em ascending}-flag. Is the flag set to ``true'',
 then the individual with the smaller fitness value will be returned, is
 the flag set to ``false'', the individual with the greater fitness
 value is returned.}
{best}
{Returns the individual with the better fitness values.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{worst!( Individual\& ind0, Individual\& ind1 )}
\setConstInstance
\setCorrectWidthThree{8pt}
\setParamOne{ind0}{Individual\&}{First individual.}
\setParamTwo{ind1}{Individual\&}{Second individual.}
\printMethodWithParamsSaved
{Individual\&}
{The individual with the ``worst'' fitness value according
 to {\em ascending}-flag. Is the flag set to ``true'',
 then the individual with the greater fitness value will be returned, is
 the flag set to ``false'', the individual with the smaller fitness
 value is returned.}
{worst}
{Returns the individual with the worst fitness values.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\subsection{Sorting Method}

%---------------------------------------------------------------------------%
\index{sortIndividuals!( vector$<$ Individual$\ast$ $>$\& indvec )}
\setNormalInstance
\printMethodWithOneParam
{void}
{sortIndividuals}
{vector$<$ Individual $\ast$ $>$\&}
{indvec}
{Vector with individuals to be sorted.}
{Sorts all individuals in {\em indvec} according to
 {\em ascending}-flag. Is the flag set to ``true'', then all individuals
 are sorted by ascending fitness, otherwise by descending fitness.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\clearpage

\subsection{Selection Methods}

%---------------------------------------------------------------------------%
\index{selectElitists!( Population\& parents, unsigned numElitists )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{parents}{Population\&}{Parent population.}
\setParamTwo{numElitists}{unsigned}{Number of elitists.
If {\em numElitists} is greater than the number
of individuals in {\em this}, then only as many elitists are sought as
{\em this} contains individuals.}
\printMethodWithParamsSaved
{void}
{}
{selectElitists}
{Looks for {\em numElitists}
 individuals with the best fitness values and copies them to the
 beginning of the population {\em this}. The selection probability
 of the parent individuals and the elitists will be adapted.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{selectRouletteWheel!( Population\& parents, unsigned numElitists )}
\setNormalInstance
\setCorrectWidthThree{8pt}
\setParamOne{parents}{Population\&}{The parent population, from which
the elitists are chosen.}
\setParamTwo{numElitists}{unsigned}{Number of elitists to be
selected.}
\printMethodWithParamsSaved
{void}
{}
{selectRouletteWheel}
{Selects {\em numElitists} individuals from the parent population
 {\em parents} as elitists and stores them at the beginning of the
 population {\em this}. The basic idea behind this selection
 method is a spinning roulette wheel. Depending on the value of the 
 {\em spinOnce}-flag, the wheel can be spinned several times
 (flag = ``false'') which is similar to a stochastic selection or
 only one time (flag = ``true'') which is similar to a non-stochastic
 selection.
 For more information cf. \cite{Search} and \cite{Jong}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

\subsection{Input- and Output Methods}

%---------------------------------------------------------------------------%
\index{readFrom!( istream\& is )}
\setNormalInstance
\printMethodWithOneParam
{void}
{readFrom}
{istream\&}
{is}
{Input stream.}
{Replaces the data of the current population {\em this} by the data
 read from the input stream {\em is}. The data must have
 the following format:\\
    ``{\tt Population(}'',\\
    Size of the population,\\
    ``{\tt )}'', Newline,\\
    Index of the best individual, Newline,\\
    Value of the {\em subPop}-flag, Newline,\\
    Value of the {\em ascending}-flag, Newline,\\
    Value of the {\em spinOnce}-flag, Newline,\\
    Following now are the values of the single individuals inside
    the population:\\
    ``{\tt Individual(}'',\\
    Size of the current individual,\\ 
    ``{\tt )}'', Newline,\\ 
    Fitness value of the individual, Newline,\\
    Scaled fitness of the individual, Newline,\\
    Value of the {\em eval}-flag, Newline,\\
    Value of the {\em feasible}-flag, Newline,\\
    Selection probability of the individual, Newline,\\
    Number of reproductions of the individual, Newline,\\
    Value of the {\em elitist}-flag, Newline,\\
    Age of the individual, Newline,\\
    And then the data of the single chromosomes will follow:\\
    ``{\tt ChromosomeT$<$}'',\\
    Type of the current chromosome,\\ 
    ``{\tt $>$(}'',\\ 
    Number of alleles,\\    
    ``{\tt )}'', Newline,\\
    Values of the single allele values, separated by a space or
    tab character.}
{None.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{writeTo!( ostream\& os )}
\setConstInstance
\printMethodWithOneParam
{void}
{writeTo}
{ostream\&}
{os}
{Output stream.}
{Writes the data of the population to the output stream {\em os}.}
{None.}
{None.}
%---------------------------------------------------------------------------%






