\subsection{Crossover Methods}

%---------------------------------------------------------------------------%
\index{crossover!( const Chromosome\& dadChrom, const Chromosome\& momChrom, const vector$<$ unsigned $>$\& points )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromosome from which the first
allele will be assigned to {\em this}. {\em dadChrom} must contain at least
one allele, otherwise no crossover will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that must
contain the same number of alleles as {\em dadChrom}, otherwise the
method will be aborted with an error message. Additionally, {\em momChrom}
must contain at least one allele or no crossover will take place.}
    \setParamThree{points}{const vector$<$ unsigned $>$\&}{Vector that
specifies the positions in {\em this}, where a change of the current
parent chromosome will take place. The number of values in {\em points}
must be at most equal to the number of alleles of one parent
chromosome, otherwise the method will be aborted with an error message.}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {Alternately assigns the allele values of the parent chromosomes
{\em dadChrom} and {\em momChrom} to {\em this}. The values inside
{\em points} specify the indices, where a change of the parent chromosome
takes place. The size of {\em this} will be adapted to the size
of the parent chromosomes. During the crossover the first new allele for 
{\em this} is taken from {\em dadChrom}.}
{}
\setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{crossover!( Chromosome\& mate, const vector$<$ unsigned $>$\& points )}
    \setCorrectWidthThree{8pt}
    \setParamOne{mate}{Chromosome\&}{Chromosome that is used for
crossover with {\em this}. The number of alleles in
{\em mate} must be equal to the number of alleles in {\em this}, otherwise
the method will be aborted with an error message. Additionally, {\em mate}
must contain at least one allele or no crossover will take place.}
    \setParamTwo{points}{const vector$<$ unsigned $>$\&}{See above.}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {Same as above, but here the ``parent'' chromosomes are
         chromosome {\em mate} and the chromosome {\em this} itself.
         If the number of values in {\em points} is odd, than {\em this}
will receive its first allele value from {\em mate}, otherwise the first
allele will be taken from {\em this}.}
{}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{crossover!( const Chromosome\& dadChrom, const Chromosome\& momChrom, const vector$<$ bool $>$\& pos )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromosome that
must contain at least one allele, otherwise no crossover will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that must
contain the same number of alleles than {\em dadChrom}, otherwise the
method will be aborted with an error message. Additionally, {\em momChrom}
must have at least one allele or no crossover will take place.}
    \setParamThree{pos}{const vector$<$ bool $>$\&}{Vector that contains
a {\tt bool} value for each allele of {\em this}. Each value will
specify, whether a change of the parent chromosome will take place at
the current allele (``true'') or not (``false'').}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {Alternately assigns the allele values of the parent chromosomes
{\em dadChrom} and {\em momChrom} to {\em this}. {\em pos} contains
{\tt bool} values, that will be used to specify for each corresponding 
allele of
{\em this}, whether a change of the current parent chromosome
will take place or not. The size of {\em this} will be adapted to
the size of one parent chromosome. {\em this} will receive its first allele
value from {\em dadChrom}, when the first value in {\em pos} is
``false'', otherwise the first allele value is taken from {\em momChrom}.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{crossover!( Chromosome\& mate, const vector$<$ bool $>$\& pos )}
    \setCorrectWidthThree{8pt}
    \setParamOne{mate}{Chromosome\&}{Chromosome that is used for crossover 
with {\em this}. The number of alleles in {\em mate} must be
the same as in {\em this}, otherwise the method will be aborted with
an error message. Additionally, {\em mate} must contain at least one allele or
no crossover will take place.}
    \setParamTwo{pos}{const vector$<$ bool $>$\&}{See above.}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {The same as above, but here the chromosome {\em mate} and the
chromosome {\em this} itself are taken as ``parent'' chromosomes.
If the first value in {\em pos} is ``false'', then the first allele
value of {\em this} will be taken from {\em this} itself, otherwise
the first allele will be taken from {\em mate}.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{crossover!( const Chromosome\& dadChrom, const Chromosome\& momChrom, unsigned npoints, unsigned align )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromosome that
must contain at least one allele, otherwise no crossover will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that must
contain as many alleles as {\em dadChrom}, otherwise the method will be
aborted with an error message. Additionally, {\em momChrom} must have at least
one allele or no crossover will take place.}
    \setParamThree{npoints}{unsigned}{Maximum number of possible changes
of the parent chromosome. It is determined randomly, whether a change 
really takes place or not.}
    \setParamFour{align}{unsigned}{Minimum size of allele intervals, after
which a change can take place. If {\em align} has no value, it will be
set to the default value ``1'', i.e. a change of the current
parent chromosome can take place at every position.}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {Alternately assigns the allele values from the parent chromosomes
{\em dadChrom} and {\em momChrom} to {\em this}. {\em npoints} is
the maximum number of possible changes of the current parent chromosome,
{\em align} indicates the minimum allele intervals where a change
can take place. The size of {\em this} will be adapted to the
size of a parent chromosome.\\
For example: {\em this} = $< 0, 0, 0, 0, 0, 0, 0, 0, 0, 0 >$,\\
{\em dadChrom} = $< 1, 1, 1, 1, 1, 1, 1, 1, 1, 1 >$, {\em momChrom} 
= $< 2, 2, 2, 2, 2, 2, 2, 2, 2, 2 >$, {\em npoints} $= 3$, {\em align}
$= 2$. The current chromosome after a call to the method within
the given parameters: 
{\em this} = $< 1, 1, 2, 2, 2, 2, 1, 1, 2, 2 >$. Here, a change of the
parent chromosome randomly took place at positions 2, 6 and 8.
Because {\em align} was set to ``2'', a change could only took place
at positions that are a multiple of ``2''.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{crossover!( Chromosome\& mate, unsigned npoints, unsigned align )}
    \setCorrectWidthThree{8pt}
    \setParamOne{mate}{Chromosome\&}{Chromosome that is used for crossover
with {\em this}. {\em mate} must contain the same
number of alleles than {\em this}, otherwise the method will be aborted
with an error message. Additionally, {\em mate} must contain at least
one allele or no crossover will take place.}
    \setParamTwo{npoints}{unsigned}{See above.}
    \setParamThree{align}{unsigned}{See above.}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {Same as above, but here the chromosomes {\em mate} and
{\em this} itself are taken as ``parent'' chromosomes.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{crossover!( const Chromosome\& dadChrom, const Chromosome\& momChrom, const Chromosome\& posChrom )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromosome that
must contain at least one allele, otherwise no crossover will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that must
contain the same number of alleles than {\em dadChrom}, otherwise the
method will be aborted with an error message. Additionally, {\em momChrom}
must have at least one allele or no crossover will take place.}
    \setParamThree{posChrom}{const Chromosome\&}{Chromosome, that will
indicate for each allele of {\em this} whether a change of the current
parent chromosome will take place (``0'') or not (a value unequal ``0'').}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {Alternately assigns allele values from the parent chromosomes
{\em dadChrom} and {\em momChrom} to {\em this}. {\em posChrom} specifies
for each allele of {\em this}, whether a change of the current parent
chromosome will take place or not. The size of {\em this} will
be adapted to the size of a parent chromosome. If the first value
in {\em posChrom} is ``0'', then the first alleles of {\em this} will 
be taken from {\em dadChrom}.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{crossover!( Chromosome\& mate, const Chromosome\& posChrom )} 
    \setCorrectWidthThree{8pt}
    \setParamOne{mate}{Chromosome\&}{Chromosome that will be used for
crossover with {\em this}. The number of alleles contained
in {\em mate} must be the same as the number of alleles in {\em this}, 
otherwise the method will be aborted with an error message. Additionally,
{\em mate} must have at least one allele or no crossover will take place.}
    \setParamTwo{posChrom}{const Chromosome\&}{See above.}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossover}
        {Same as above, but here the chromosome {\em mate} and
{\em this} itself are taken as ``parent'' chromosomes. If the first value
of {\em posChrom} is ``0'', then the first alleles of {\em this} will
be the old alleles of {\em this} itself.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{crossoverUniform!( const Chromosome\& dadChrom, const Chromosome\& momChrom, const vector$<$ bool $>$\& pos )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromosome that must
contain at least one allele, otherwise no crossover will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that
must contain the same number of alleles than {\em this}, otherwise the
method will be aborted with an error message. Additionally, {\em momChrom}
must have at least one allele or no crossover will take place.}
    \setParamThree{pos}{const vector$<$ bool $>$\&}{Vector that indicates
for each allele of {\em this}, whether the current value will be taken
from {\em dadChrom} (``false'') or from {\em momChrom} (``true'').}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossoverUniform}
        {Alternately assigns the allele values of the parent chromosomes
{\em dadChrom} and {\em momChrom} to {\em this}. {\em pos} indicates
for each allele of {\em this}, whether the current allele value is taken
from {\em dadChrom} or {\em momChrom}. The size of {\em this} will
be adapted to the size of a parent chromosome.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{crossoverUniform!( Chromosome\& mateChrom, const vector$<$ bool $>$\& pos )}
    \setCorrectWidthThree{8pt}
    \setParamOne{mateChrom}{Chromosome\&}{Chromosome that is used for
crossover with {\em this}. The number of alleles contained
in {\em mateChrom} must be the same as in {\em this}, otherwise the
method will be aborted with an error message. Additionally, {\em mateChrom}
must have at least one allele or no crossover will take place.}
    \setParamTwo{pos}{const vector$<$ bool $>$\&}{Vector, that indicates
for each allele of {\em this}, whether the old allele value will be taken
over (``false'') or transcribed from {\em mateChrom} (``true'').}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossoverUniform}
        {Same as above, but here the chromosomes {\em mateChrom} and
{\em this} itself are taken as ``parent'' chromosomes.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{crossoverUniform!( const Chromosome\& dadChrom, const Chromosome\& momChrom )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromsome that must
contain at least one allele, otherwise no crossover will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that
must contain as many alleles as {\em dadChrom}, otherwise the method
will be aborted with an error message. Additionally, {\em momChrom}
must have at least one allele or no crossover will take place.}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossoverUniform}
        {Alternately assigns the allele values of the parent chromosomes
{\em dadChrom} and {\em momChrom} to {\em this}. For each allele of {\em this}
it will be randomly determined, whether {\em this} will receive the
current allele value from {\em dadChrom} (probability = $0.5$) or 
{\em momChrom} (probability = $0.5$). The size of {\em this} will
be adapted to the size of a parent chromosome.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{crossoverUniform!( Chromosome\& mateChrom )}
    \printMethodWithOneParam
    {void} 
    {crossoverUniform}
    {Chromosome\&} 
    {mateChrom} 
    {Chromosome that is used for crossover with {\em this}.
The size of {\em mateChrom} must be equal to the size of {\em this},
otherwise the method will be aborted with an error message. Additionally,
{\em mateChrom} must contain at least one allele or no crossover will take
place.}
    {Same as above, but here the chromosomes {\em mateChrom} and {\em this}
itself are taken as ``parent'' chromosomes.}
    {None.}
    {None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{crossoverUniform!( const Chromosome\& dadChrom, const Chromosome\& momChrom, const Chromosome\& posChrom )}
    \setCorrectWidthThree{8pt}
    \setParamOne{dadChrom}{const Chromosome\&}{Father chromosome that must
contain at least one allele, otherwise no crossover will take place.}
    \setParamTwo{momChrom}{const Chromosome\&}{Mother chromosome that must
contain as many alleles as {\em dadChrom}, otherwise the method will be
aborted with an error message. Additionally, {\em momChrom} must have
at least one allele or no crossover will take place.}
    \setParamThree{posChrom}{const Chromosome\&}{Chromosome which 
indicates, whether the current allele value will be
taken from {\em dadChrom} (``0'') or {\em momChrom} (a value unequal ``0'').}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossoverUniform}
        {Alternately assigns the allele values of the parent chromosomes
{\em dadChrom} and {\em momChrom} to {\em this}. {\em posChrom} indicates
for each allele of {\em this}, whether {\em this} will receive its
current allele value from {\em dadChrom} or {\em momChrom}. The size of {\em this} will be adapted to the size of a parent chromosome.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{crossoverUniform!( Chromosome\& mateChrom, const Chromosome\& posChrom )}
    \setCorrectWidthThree{8pt}
    \setParamOne{mateChrom}{Chromosome\&}{Chromosome that is used for
crossover with {\em this}. {\em mateChrom} must contain
the same number of alleles as {\em this}, otherwise the method will be
aborted with an error message. Additionally, {\em mateChrom} must
have at least one allele or no crossover will take place.}
    \setParamTwo{posChrom}{const Chromosome\&}{Chromosome which 
indicates, whether the current allele value of {\em this} will be taken
from \\{\em mateChrom} (a value unequal ``0'') or the old value of {\em this}
will be taken over (``0'').}
    \printMethodWithParamsSaved
        {void}
        {}
        {crossoverUniform}
        {Same as above, but here the chromosomes {\em mateChrom} and
{\em this} itself will be taken as ``parent'' chromosomes.}
        {}
    \setCorrectWidthThree{4pt}
%---------------------------------------------------------------------------%
