\subsection{Information Retrieval Methods}

%---------------------------------------------------------------------------%
\index{size!( )}
\setConstInstance
\printEmptyMethodReturn
{unsigned}
{size}
{Returns the number of individuals in {\em this}.}
{Number of individuals in {\em this}.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{ascendingFitness!( )}
\setNormalInstance
\printEmptyMethodReturn
{bool}
{ascendingFitness}
{Returns whether the individuals inside {\em this} are
 sorted by ascending or descending fitness values.}
{Value of the {\em ascending}-flag:\\
 {\em true} - The individuals are sorted by ascending fitness values,\\
                    {\em false} - The individuals are sorted by descending
 fitness values.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{minFitness!( )}
\setConstInstance
\printEmptyMethodReturn
{double}
{minFitness}
{Returns the minimum fitness value inside {\em this}.}
{Minimum fitness value of the population or $0.0$, if the population
 is empty.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{maxFitness!( )}
\setConstInstance
\printEmptyMethodReturn
{double}
{maxFitness}
{Returns the maximum fitness value inside {\em this}.}
{Maximum fitness value of the population or $0.0$, if the population
 is empty.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{meanFitness!( )}
\setConstInstance
\printEmptyMethodReturn
{double}
{meanFitness}
{Returns the mean fitness value of the population's individuals.}
{The mean fitness value of the population or $0.0$ if the population
 is empty.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{stdDevFitness!( )}
\setConstInstance
\printEmptyMethodReturn
{double}
{stdDevFitness}
{Returns the standard deviation of all fitness values of the population
 computed as $\sigma = \frac{1}{n}\sum_{i=0}^{n-1}{[f(this_i) - 
 \overline{f(this_i)}]}^2$ with $n\ =\ |this|$. {\em f} is the function 
 that evaluates
 the fitness of an individual.}
{Standard deviation of all fitness values or $0.0$, if the population
 is empty.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{bestIndex!( )}
\setConstInstance
\printEmptyMethodReturn
{unsigned}
{bestIndex}
{Returns the index of the individual with the best fitness value.
 The best fitness value depends on the value of the {\em ascending}-flag.
 If {\em ascending} is set to ``true'', the minimum fitness value
 is the best, if {\em ascending} is set to ``false'', the maximum
 fitness value is the winner. The population must contain at least
 one individual, otherwise the method will be aborted with an error
 message. This method also works properly, when the individuals are
 not already sorted.}
{Index of the individual with the best fitness value.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{worstIndex!( )}
\setConstInstance
\printEmptyMethodReturn
{unsigned}
{worstIndex}
{Returns the index of the individual with the worst fitness value.
 The worst fitness value depends on the value of the {\em ascending}-flag.
 If {\em ascending} is set to ``true'', the maximum fitness value
 is the worst, if {\em ascending} is set to ``false'', the minimum
 fitness value is the looser. The population must contain at least
 one individual, otherwise the method will be aborted with an error
 message. This method also works properly, when the individuals are
 not already sorted.}
{Index of the individual with the worst fitness value.}
%---------------------------------------------------------------------------%

\clearpage

%---------------------------------------------------------------------------%
\index{best!( )}
\setNormalInstance
\printEmptyMethodReturnSpecial
{Individual\&}
{best}
{Same as above (method {\em bestIndex}), but here not only the index
 of the best individual, but the individual itself is returned.}
{Individual with the best fitness value.}
{None.}
%---------------------------------------------------------------------------%

\vspace*{4ex}

%---------------------------------------------------------------------------%
\index{worst!( )}
\setNormalInstance
\printEmptyMethodReturnSpecial
{Individual\&}
{worst}
{Same as above (method {\em worstIndex}), but here not only the index
 of the worst individual, but the individual itself is returned.}
{Individual with the worst fitness value.}
{None.}
%---------------------------------------------------------------------------%








